---
title: "Hw8"
format: html
editor: visual
---

## Reading Data

Reading in the Seoul bike sharing data set, using locale argument to fix error with element 1.
```{r}
library(tidyverse)
bike <- read_csv("https://www4.stat.ncsu.edu/~online/datasets/SeoulBikeData.csv", locale=locale(encoding="latin1"))
```

## EDA
### Checking the Data

To start, we need to check our data set and prepare it for use in generating models. First we check for any missing values. 
```{r}
colSums(is.na(bike))
```

It appears there are no missing values in the dataset. Next we will check the types of data in each column, as well as show summary stats for each numeric column and levels for categorical columns.
```{r}
str(bike)
summary(bike)
lapply(bike, function(x) if(is.character(x) || is.factor(x)) unique(x))
```

Now that we have a good idea of the structure of the data as well as the kind of values we see for both numeric and categorical variables, lets convert the Date column to the Date type of data.
```{r}
bike <- bike |> mutate(Date = dmy(Date))
```

The Date column is now a Date type of data. Now we should convert the other character data columns into factor data.
```{r}
bike <- bike |> mutate(across(where(is.character), as.factor))
```
